Validation failed EVT

### 2022-07-28 analysis/article-results.Rmd
Rmd including figure exports

```{r miss-dat-summ}
# Visualise missings beforehand
naniar::gg_miss_var(dat_to_impute, facet = dataset, show_pct = TRUE)
naniar::gg_miss_upset(dat_valid, nsets = 10)
naniar::gg_miss_upset(dat_develop, nsets = 10)
```

@@

@@

Bootstrap-based internal validation, optimism-corrected performance:

@@

Calibration plot (apparent)

@@

@@

(Ewout reference here, article)

@@

@@

>>>>

The next plots look at the combinations of variables missings and their frequencies in the development and validation sets respectively:

```{r miss-dat-summ}
# Visualise missings beforehand
naniar::gg_miss_var(dat_to_impute, facet = dataset, show_pct = TRUE)
naniar::gg_miss_upset(dat_develop, nsets = 10, )
naniar::gg_miss_upset(dat_valid, nsets = 10)
```

@@

Coefficients of the (penalized, with Ridge) prediction model built using the development data:

@@

Bootstrap-based internal validation, optimism-corrected performance of this model:

@@

Calibration plot, reflecting apparent performance:

@@

At external validation, the calibration plot shows that there is quite some overestimation of risks in the validation set.

@@

See [Balmaña, Stockwell, Steyerberg et al. (2006)](https://jamanetwork.com/journals/jama/article-abstract/203427). Here, we use standard (unpenalized) logistics regression to test for differences between the development and validation set in terms of multivariable model coefficients.

The log odds table of coefficient, and the p-values for the interaction:

@@

In the format of Table 4 from the article mentioned above (with odds ratios):

```{r inter-steyerberg}
# Second attempt in Ewout format 
# 
library(broom.helpers)
library(broom)

dev_unpen <- split(imps_combined |> 
                     filter(dataset == "develop"), ~ .imp) |> 
  map(.f = ~ glm(model_formula, family = binomial, data = .x)) |> 
  mice::pool() |> 
  #broom::tidy(exponentiate = TRUE, conf.int = TRUE) |> 
  tidy(exponentiate = TRUE, conf.int = TRUE) |> 
  #tidy_add_reference_rows(no_reference_row = all_categorical())
  mutate(
    "Development" = paste0(
      round(estimate, 3), " [",
      round(conf.low, 3), ", ",
      round(conf.high, 3), "]"
    )
  ) |> 
  select(term, Development)

valid_unpen <- split(imps_combined |> 
                     filter(dataset == "valid"), ~ .imp) |> 
  map(.f = ~ glm(model_formula, family = binomial, data = .x)) |> 
  mice::pool() |> 
  #broom::tidy(exponentiate = TRUE, conf.int = TRUE) |> 
  tidy(exponentiate = TRUE, conf.int = TRUE) |> 
  #tidy_add_reference_rows(no_reference_row = all_categorical())
  mutate(
    "Validation" = paste0(
      round(estimate, 3), " [",
      round(conf.low, 3), ", ",
      round(conf.high, 3), "]"
    )
  ) |> 
  select(term, Validation)

comb_unpen <- split(imps_combined, ~ .imp) |> 
  map(.f = ~ glm(model_formula, family = binomial, data = .x)) |> 
  mice::pool() |> 
  #broom::tidy(exponentiate = TRUE, conf.int = TRUE) |> 
  tidy(exponentiate = TRUE, conf.int = TRUE) |> 
  #tidy_add_reference_rows(no_reference_row = all_categorical())
  mutate(
    "Combined" = paste0(
      round(estimate, 3), " [",
      round(conf.low, 3), ", ",
      round(conf.high, 3), "]"
    )
  ) |> 
  select(term, Combined)

cbind.data.frame(
  "Term" = dev_unpen$term, 
  "Development \n cohort" = dev_unpen$Development, 
  "Validation \n cohort" = valid_unpen$Validation,
  "Combined \n cohort" = comb_unpen$Combined
) |> 
  DT::datatable(
  extensions = 'Buttons',
  options = list(
    dom = 'Blfrtip', 
    buttons = c('csv', 'excel', 'pdf'),
    lengthMenu = list(c(10, 25, 50, -1), c(10, 25, 50, "All"))
  )
)
```

@@

```{r nom-export, results='hide'}
png(
  filename = "analysis/figures/nomogram-combined.png",
  width = 8,
  height = 11,
  units = "in",
  res = 300
)
plot(nom)
dev.off()

# Predict max prob
newpat <- dat_nomogram[1, ]
newpat$ArchElongation <- "III"
newpat$AngleFollowingBifurcation <- "Yes, angle >=90 degrees"
newpat$InnCca_nr_90orLarger <- ">=1"
newpat$ICAE_NASCET_Degree <- ">=99"
newpat$M_age <- 8
newpat

predict(mod_lrm, type = "fitted", newdata = newpat)
```
